---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# qbinplots

<!-- badges: start -->

[![CRAN status](https://www.r-pkg.org/badges/version/qbinplot)](https://CRAN.R-project.org/package=qbinplot) [![R-CMD-check](https://github.com/edwindj/qbinplot/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/edwindj/qbinplot/actions/workflows/R-CMD-check.yaml)

<!-- badges: end -->

This package is in its early stages, not ready for production yet.

## Installation

You can install the development version of `qbinplot` from [GitHub](https://github.com/) with:

``` r
remotes::install_github("edwindj/qbinplots")
```

## Example

```{r example}
library(qbinplots)
## basic example code
```

A quantile binning boxplot

```{r percentile_iris}
qbin_boxplot(iris, "Sepal.Length", n = 25, auto_fill = TRUE)
```

vs

A quantile binning barplot

```{r}
qbin_barplot(iris, "Sepal.Length", 25, auto_fill = TRUE)
```

```{r}
table_plot(iris, "Sepal.Length", 25, auto_fill = TRUE)
```

```{r}
funq_plot(iris, "Sepal.Length", 25, auto_fill = TRUE)
```

Choosing "Petal.Width"

```{r}
qbin_boxplot(iris, "Petal.Width", 25, auto_fill = TRUE)
```

```{r qbin_boxplot_penquins}
library(palmerpenguins)
qbin_boxplot(penguins[1:7], c("body_mass_g"), 25)
```


Or the well-known `diamonds` dataset

```{r}
data("diamonds", package = "ggplot2")
table_plot(diamonds[1:7], "carat")
```

```{r}
data("diamonds", package = "ggplot2")
qbin_boxplot(diamonds[1:7], "carat")
```

```{r}
funq_plot(diamonds[1:7], "carat")
```

We can zoom in on the `carat` variable, because the upper quantile bins are not very informative.
```{r}
funq_plot(
  diamonds[1:7], 
  "carat", 
  auto_fill = TRUE,
  xlim = c(0, 2.5)
)
```

```{r}
qbin_heatmap(
  iris,
  x = "Sepal.Length",
  n = 25
)
```

